Gammapy: A Python package for gamma-ray astronomy

### 2023-06-11 src/ms-review.tex
Apply suggestions from code review
Co-authored-by: Atreyee Sinha <asinha@ucm.es>

In addition to the instrument characteristics described above, there is also the instrumental
background, that results from hadronic events being misclassified as \gammaray events. These
events constitute a uniform background to the \gammaray events. For \fermi the residual hadronic background
is very small ($<1\%$) because of its veto layer and can often be neglected. For IACTs and WCTs in contrast
the background can account for a very large part ($>95\%$) of the events and must be treated
accordingly in the analysis. As the background is very specific to the instrument, \gammapy typically 
relies on the background models provided with the DL3 data. The background typically only depends
on the reconstructed event position and energy $Bkg(p, E)$. However in general all IRFs depend on the
geometrical parameters of the detector, e.g. location of an event in the FoV or the elevation
angle of the incoming direction of the event. Consequently IRFs might be parametrised as functions
of detector specific coordinates as well.

>>>>

In addition to the instrument characteristics described above, there is also the instrumental
background, that results from hadronic events being misclassified as \gammaray events. These
events constitute a uniform background to the \gammaray events. For \fermi the residual hadronic background
is very small ($<1\%$) because of its veto layer and can often be neglected. For IACTs and WCDs in contrast,
the background can account for a very large part ($>95\%$) of the events and must be treated
accordingly in the analysis. As the background is very specific to the instrument, \gammapy typically 
relies on the background models provided with the DL3 data. The background typically only depends
on the reconstructed event position and energy $Bkg(p, E)$. However in general all IRFs depend on the
geometrical parameters of the detector, e.g. location of an event in the FoV or the elevation
angle of the incoming direction of the event. Consequently IRFs might be parametrised as functions
of detector specific coordinates as well.
